Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-10-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

\subsection{The case studies and the Algorithm}
It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (1,200 W inverter, but with autonomy of just 6 h). 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

However, related to the results of the automated verification, the 1,200 W PV system failed during the sizing check. The number of panels in series was not the correct (the verification indicates 3 panels in series and the project has 2 in series and 2 in parallel). That verification took 3 days to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).

And related to the four 700 W PV system, the sizing check was successful, but all the fail occurred during battery autonomy verification. XXXXXXX

>>>>

\subsection{The case studies and the Algorithm}
It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was not correct (the verification indicates 3 panels in parallel and the project has 2 in series and 2 in parallel). That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). But it is understandable that this problem occurs because the system was purchased as a off-the-shelf solution and not as a specific design for the electrical charges of the house.

And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%. The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries. The framework took 409.3 hours to found an error at house 1, and the maximum of 456XXX hours to house 4.
